Computer Science House By-Laws

### 2016-11-13 bylaws.tex
updated text

At any point before the Introductory Evaluation, an Introductory Member may make a second attempt at the Introductory Packet by requesting a new Introductory Packet from the Evaluations Director. Then, the Introductory Member goes through the \ref{Creation of Accounts} proccess once again. The results of the new Introductory Packet will also affect the number of signatures evaluated at the Introductory Evaluations. 

>>>>

At any point before the Introductory Evaluation, an Introductory Member may make a second attempt at the Introductory Packet by requesting a new Introductory Packet from the Evaluations Director. Then, the Introductory Member goes through the \ref{Creation of Accounts} proccess once again. The results of the new Introductory Packet will replace the results of the first attempt to be evaluated at the Introductory Evaluations (if the score is improved. If the results of packet the did not improve, the original packet score is evaluated).
